Contracts for Contracts

### 2023-07-09 paper/background.tex
background section [WIP]

% blockchain in a nutshell (keep it short)
\paragraph{Ethereum}
% \textit{Ethereum}~\cite{buterin2014next} is a blockchain platform designed to be more flexible and programmable than its predecessor, \textit{Bitcoin}~\cite{nakamoto2008bitcoin}. 
Ethereum~\cite{buterin2014next} is a blockchain platform designed to  provide better flexibility and programmability than its precursor, Bitcoin~\cite{nakamoto2008bitcoin}.
There are two types of accounts in the Ethereum blockchain: \textit{Externally Owned Accounts} (EOAs) and \textit{Smart Contracts}. 
EOAs, controlled by private keys, usually stand for individual users. Meanwhile, smart contracts are self-running programs that enforce agreements without needing a third party. 
Actions on Ethereum are conducted through \textit{Transactions}, mostly involving interactions with smart contracts (e.g., invoking a function of a smart contract).

% Solidity in a nutshell
\paragraph{Solidity}
Solidity, a widely used programming language for smart contracts, shares syntax similarities with Java and JavaScript. 
In Solidity, a contract acts much like a class in Java, and it can contain data fields. 
The language allows functions with modifiers such as \texttt{external}, implying that a function can be invoked by an EOA or another contract, and \texttt{internal}, indicating that only other functions within the contract can call this function. 
Solidity compiler compiles a contract into bytecode.
When the bytecode is sent to the blockchain, the corresponding contract gets deployed.

% compilation --> deployment --> address --> high-order --> open world (boundry)
\paragraph{Address}
Both EOAs and Smart Contracts can be identified by a unique 160-bit address. 
the address of an EOA comes from its private key, while the one of a smart contract is decided by how the contract is deployed.

Addresses in Solidity are not just first-class values but also callable and capable of conducting complex computations. 
They play a crucial role in Solidity, enabling complex higher-order computations, flexible interactions, and efficient access control for smart contracts. 
The following example will provide an insight into how addresses are used in Solidity.

>>>>

% blockchain in a nutshell (keep it short)
\paragraph{Ethereum}
% \textit{Ethereum}~\cite{buterin2014next} is a blockchain platform designed to be more flexible and programmable than its predecessor, \textit{Bitcoin}~\cite{nakamoto2008bitcoin}. 
Ethereum~\cite{buterin2014next} is a blockchain platform designed to  provide better flexibility and programmability than its predecessor, Bitcoin~\cite{nakamoto2008bitcoin}.
There are two types of accounts in the Ethereum blockchain: \textit{Externally Owned Accounts} (EOAs) and \textit{Smart Contracts}. 
EOAs, controlled by private keys, usually stand for individual users. Meanwhile, smart contracts are self-running programs that enforce agreements without needing a third party.
Actions on Ethereum are conducted through \textit{Transactions}, mostly involving interactions with smart contracts (e.g., invoking a function of a smart contract).

% Solidity in a nutshell
\paragraph{Solidity}
Solidity, a widely used programming language for smart contracts, shares syntax similarities with Java and JavaScript. 
In Solidity, a contract acts much like a class in Java, and it can contain data fields. 
The language allows functions with modifiers such as \texttt{public}, implying that a function can be invoked by an EOA or another contract, and \texttt{private}, indicating that only other functions within the contract can call this function. 
Solidity compiler compiles a contract into bytecode.
When the bytecode is sent to the blockchain, the corresponding contract gets deployed.

% compilation --> deployment --> address --> high-order --> open world (boundry)
\paragraph{Address}
Both EOAs and smart contracts can be identified by a unique 160-bit address. 
An EOA's address is derived from its private key, while the address of a smart contract comes from its deployment process.

In Solidity, addresses not only exist as first-class values but are also callable entities capable of carrying out complex computations. 
The importance of addresses is highlighted by their function in supporting sophisticated higher-order computations, enabling flexible interactions, and facilitating efficient access control for smart contracts. \zz{discuss the improtrance of addresses after explaning the example.}
The following example provides an insight into how addresses are used in Solidity.
